%\documentclass[a4paper,12pt,oneside,openany]{jsbook}
%\include{begin}

%\chapter*{概要}
%\addcontentsline{toc}{chapter}{概要}
\chapter{Abstract}
The J-PARC E40 experiment succeeded in measuring the differential cross-sections of the $\SPMp$ scattering and $\SMpLn$ inelastic scattering at the J-PARC Hadron Experimental Facility from 2018 to 2020. Next, to offer precise experimental data on the $\LN$ channel, we planned the next-generation $\Lp$ scattering experiment (J-PARC E86) where the beam $\Lambda$ derived from the $\PiKL$ reaction will cause $\Lp$ scattering. 

The J-PARC E86 aims to measure the differential cross-section and spin observables such as an analyzing power $\anapow$ and a depolarization $\depo$ of $\Lp$ scattering. The beam $\Lambda$ should be almost 100\% polarized toward the spin observables measurement, and we need to know its polarization value to obtain these observables. Due to the prohibition of ALS for the isospin symmetry in the $NN$ channels and the experimental difficulty of $YN$ scattering, the experimental data of these spin observables are historically lacking. They can probe into the SLS (ALS) and tensor force \cite{Ishikawa-2004}. Therefore, this measurement in the J-PARC E86 could restrict the present $\BB$ interaction models. 

As a basic study for J-PARC E86, the $\PiKL$ reaction data with $1.32$ GeV/$c$ $\pM$ beam accumulated in J-PARC E40 was analyzed. Its experimental setup was almost the same as J-PARC E86. J-PARC E40 was performed using the cylindrical detector cluster (CATCH) and the forward magnetic spectrometer (KURAMA) at the J-PARC K1.8 beamline in the J-PARC Hadron Experimental Facility. It measured the differential cross-sections of $\SPMp$ scatterings and $\SMpLn$ inelastic scattering with a high intensity $\pi$ beam of $20$ M/spill ($1$ spill $= 5.2$ sec with a beam duration of $2$ sec) at beam momentum of $1.41$ GeV/$c$ for a $\pP$ beam, and $1.33$ GeV/$c$ for a $\pM$ beam, respectively. Owing to a kinematical consistency analyses, J-PARC E40 succeeded in tagging the produced $\Sigma^{\pm}$s: $4.9\times10^7$ $\SP$s, and $1.62\times10^7$ $\SM$s. Using these momentum-tagged $\Sigma^{\pm}$ beams, the differential cross-sections were measured in the momentum range of $440 - 800$ MeV/$c$ ($\SPp$ scattering), $470 - 850$ MeV/$c$ ($\SMp$ scattering), and $470 - 650$ MeV/$c$ ($\SMpLn$ inelastic scattering) \cite{Nana-SPp} \cite{Miwa-SMp} \cite{Miwa-SMLn}. 

In this paper, we requested a cylindrical detector cluster (CATCH) to detect two cases: (1) two protons with/without one $\pM$ and (2) one proton and one $\pM$. Here, the $\Lp$ scattering identification (case \rom{1}) and beam $\Lambda$ polarization measurement (case \rom{2}) were performed. 
In $\Lp$ scattering identification, we also applied a detection option regarding the presence or absence of $\pM$ decayed from scattered $\Lambda$. We found that in the case without decay $\pM$, at least 43 counts of $\Lp$ scattering events were identified with S/N$=11.678$. In the case with decay $\pM$, we finally identified at least 15 counts of $\Lp$ scattering events with a high accuracy of S/N$=17.9785$. Therefore, it was concluded that the $\Lp$ scattering identification method developed this time can be applied to J-PARC E86, and it will be possible to measure the differential cross-sections with higher statistics and higher accuracy.
The beam $\Lambda$ polarization was performed in the $\Kz$ scattering angle range of $0.6<\costkz<1.0$ with an angular step of $d\costkz=0.05$. It was obtained by measuring the emission angle distribution of decay protons in the rest frame of $\Lambda$ ($\costp$). Finally, we confirmed that the average polarization in the angle region of $0.6<\costkz<0.8$ is high: $\PL=0.94\pm0.065$. Therefore, we concluded that by selecting this specific $\Kz$ scattering angle range in the J-PARC E86 experiment, it is possible to measure spin observables using a nearly 100\% polarized beam $\Lambda$.

Based on the $\Lp$ scattering identification and beam $\Lambda$ polarization measurement methods established in this paper, J-PARC E86 would measure the differential cross-section and spin observables of $\Lp$ scattering. Since the experimental data on the $\LN$ channel are still lacking, it could be an essential input for establishing more realistic $\BB$ interaction models beyond the problem that current models have been built based on $NN$ scattering data and a few hyperon-proton scattering data. 

%\include{end}
